Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-01 paper/main.tex
Resolve comments

\todo[inline]{das Verschieben des Sounds in den Segmenten spiegelt sich auch in
den unterschiedlichen Counts der Events je Segment (s. Tabelle 1 \& 3) wider (AV
Bild vs AV Sound vs AO Sound)}

@@

% movie events
The events of the movie cut related categories and \texttt{no\_cut} events were
modeled as impulse events.\todo{box car of 200 ms starting with the cut}.
%
Nouns were modeled from onset to offset of each word, low-level confounds from
onset to offset of the corresponding movie frame AO:
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.
% convolving
Events for all regressors of the AV and AO stimulus were convolved with a double
gamma hemodynamic response function (HRF).
% we checked correlations
Since we annotated events in naturalistic stimuli and thus fixed time courses
that could not experimentally manipulated, the modeled time-series [of
hemodynamic activity] based on these events could be correlated leading to
shared variance and thus low detection power of subsequent analyses.
% correlations within stimuli and across stimuli
Hence, we tested for correlation of regressors across the eight segments of each
stimulus and also for correlations of regressors across both stimuli (s. Figure
\ref{fig:reg-corr})
% correlations within each stimulus
The computed Pearson correlation coefficients demonstrate no to minor
correlations of modeled hemodynamic time-series belonging to the same stimulus.
% (highest) correlations across stimuli
The highest correlations are apparent between auditory low-level confounds
across stimuli (\texttt{fg\_av\_ger\_rms} and \texttt{fg\_ad\_rms}, r=.7635;
\texttt{fg\_av\_ger\_lrdiff} and \texttt{fg\_ad\_lrdiff} and , r=.7749).
% no surprise
This was expected and served as a ``sanity check'' since the audio-track of the
audio-description is the audio-track of the movie but featuring the additional
narrator (s. Figure \ref{fig:reg-corr}).
% encouraged by that we build contrasts (statement)
As a result, we felt encouraged to create voxel-wise GLM $t$-contrasts similarly
to previous studies that used controlled stimuli.

@@

% AD intro
Second, we analyzed data from the audio-description offering exclusively
auditory stimulation.
% AD primary contrast
The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
non-spatial noun categories) yielded six significant clusters (see Table
\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
% overlap with ROI
Two homologous clusters are located in the anterior part of the PPA group
overlap that we gained from the visual localizer experiment.
% in detail
Specifically, these clusters are located at the borders of the posterior
parahippocampal cortex, the occipital and temporal fusiform gyrus and lingual
gyrus.\todo{Havard-Oxford atlas gives 3 different most prob. locations depen.
on voxel}
% precuneus
Two additional clusters are apparent in the ventral precuneus extending into the
retrosplenial cortex.
% LOC
Finally, two homologous clusters are located in the superior lateral occipital
cortex.
% concluding statement
\todo[inline]{any concluding statement here or merely report the clusters?}

@@

% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to \citep{sengupta2016extension}, we used the same contrast of each
naturalistic stimulus and the same threshold for all subjects (Z>2.3, p<.05
cluster-corrected for the analysis in subject-space; Z>3.4, p<.05 for the
analysis in group-space).
% subject space -> NeuroVault
Results of the analyses that were performed in subject-space can be found in the
accompanying dataset. \todo{Neurovault does not like unstandardized spaces}
% here report in group space
For better comparisons of subjects, we here report results from the analyses
performed in group space.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AV
and AD $t$-contrast, and the outline of overlapped, individual PPAs
\citep{sengupta2016extension}.
% MNI space
The $z$-maps and PPA outline are overlayed on the co-registered MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts [at least some] voxels of
significant clusters in almost all subjects.

@@

\todo[inline]{BA-plots only shortly mentioned now}
% Bland-Altman-Plots
To better depict the agreement and difference between the results of the visual
localizer and the primary AD contrast, we created a Bland-Altman-Plot for every
subject (see ).
% what it depicts
Each subplot of Figure \ref{fig:bland-altman} visualizes the mean value and
difference (localizer minus AD) of two spatially corresponding voxels in the
unthresholded $z$-maps.
% top KDE plot
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (see KDE plot for the x-axis).
% right KDE plot
Values above the horizontal line depict voxels that show a higher $z$-value in
the dedicated localizer, values below the horizontal line depict voxels that
show higher $z$-value in the AD stimulus.

@@

\todo[inline]{I tried to keep following part concise but detailed; individual
contrasts are given but as numbers}

@@

% AV
In order to test the robustness of our findings, we created four additional
$t$-contrasts for the AV stimulus (see Table \ref{tab:av-contrasts}) to be
investigated on a group level.
% results: PPA; biggest overlap in posterior part of PPA group overlap  =
%temporal occipital fusiform cortex
All of the overall five AV contrasts yielded significant bilateral clusters that
overlap with the PPA group overlap (see Figure \ref{fig:stability-slices}).
% AD
For the AD stimulus, we created overall eight $t$-contrasts (see Table
\ref{tab:ao-contrasts}).
% results
All contrasts except contrast 7 (\texttt{se\_new}, \texttt{se\_old} >
non-spatial categories) and contrast 8 (\texttt{se\_new} > non-spatial
categories) yielded significant bilateral clusters in anterior regions of the
group PPA overlap (see Figure \ref{fig:stability-slices}).
% statement/answer
Results suggest that our findings are robust across differently designed
contrasts.\todo{concluding statement
often feels like interpretation}

@@

% AD stimulus
In the analysis of the AD data, we created control contrasts based on events of
the annotated movie cuts (cf. Table \ref{tab:ao-contrasts})
% contrast 9
Contrast 9 (vse\_new > pe\_old) revealed one significant cluster in the left
inferior prefrontal cortex (pars triangularis) and right ventral
precuneus/posterior cingulate gyrus.
% contrast 12
Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
one cluster in the right posterior hippocampus. \todo{definitively hippocampus,
dorsally of PPA}

@@

% optimal stimulus type in vision
In the visual domain, landscapes and not pictures of landmarks or buildings are
considered to be the ``optimal'' stimulus type
\citep{epstein2008parahippocampal}.\todo{a review}
% we did not choose se\_new and se\_old
We did not include the categories that contained switches from one setting to
another (\texttt{se\_new} and \texttt{se\_old}) which one might assume to
contain the auditory equivalent to the ``optimal'' visual stimulus type in the
primary AD contrast.
% why
The reason was that the categories \texttt{se\_new} and \texttt{se\_old} were
heterogeneous: they rarely contained holistic (but also vague) descriptions of
landscapes (e.g.  ``[Forrest is running through the] jungle'') but mostly
landmarks or buildings, and also non-spatial hints (e.g. ``[Jenny as a]
teenager``).
% further studies
Given that humans can identify the gist of a rich visual scene within the
duration of a single fixation \citep{henderson2003human} further studies might
investigate if vague verbal descriptions of landscapes lead to a different
hemodynamic activity level than descriptions of more concrete parts of a scene
(e.g.``[a] beacon'', [a] ``farmhouse'').

@@

lore ipsum

\section{Conclusions}

\todo[inline]{SE: frage ich mich das beim Durchgehen: Warum ist der Fokus so
sehr auf Audiobook / AD, während AV doch eigentlich more natural and engaging
ist? COH: at the moment, the discussion is not tailored to the topic
``naturalistic stimulus as substitute to localizer'' as it is not and should not
be the main focus}

\todo[inline]{template has no section ``conclusion'' -> use the last paragraph}

>>>>

@@

% movie events
The events of the movie cut related categories and \texttt{no\_cut} events were
modeled as box car events of 200 ms duration.
%
Nouns were modeled from onset to offset of each word, low-level confounds from
onset to offset of the corresponding movie frame AO:
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.
% convolving
Events for all regressors of the AV and AO stimulus were convolved with a double
gamma hemodynamic response function (HRF).
% we checked correlations
Since we annotated events in naturalistic stimuli and thus fixed time courses
that could not experimentally manipulated, the modeled time-series [of
hemodynamic activity] based on these events could be correlated leading to
shared variance and thus low detection power of subsequent analyses.
% correlations within stimuli and across stimuli
Hence, we tested for correlation of regressors across the eight segments of each
stimulus and also for correlations of regressors across both stimuli (s. Figure
\ref{fig:reg-corr})
% correlations within each stimulus
The computed Pearson correlation coefficients demonstrate no to minor
correlations of modeled hemodynamic time-series belonging to the same stimulus.
% (highest) correlations across stimuli
The highest correlations are apparent between auditory low-level confounds
across stimuli (\texttt{fg\_av\_ger\_rms} and \texttt{fg\_ad\_rms}, r=.7635;
\texttt{fg\_av\_ger\_lrdiff} and \texttt{fg\_ad\_lrdiff} and , r=.7749).
% no surprise
This was expected and served as a ``sanity check'' since the audio-track of the
audio-description is the audio-track of the movie but featuring the additional
narrator (s. Figure \ref{fig:reg-corr}).
% encouraged by that we build contrasts (statement)
As a result, we felt encouraged to create voxel-wise GLM $t$-contrasts similarly
to previous studies that used controlled stimuli.

@@

% AD intro
Second, we analyzed data from the audio-description offering exclusively
auditory stimulation.
% AD primary contrast
The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
non-spatial noun categories) yielded six significant clusters (see Table
\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
% overlap with ROI
Two homologous clusters are located in the anterior part of the PPA group
overlap that we gained from the visual localizer experiment.
% in detail
Specifically, these clusters are located at the borders of the posterior
parahippocampal cortex, the occipital and temporal fusiform gyrus and lingual
gyrus.\todo{Havard-Oxford atlas gives 3 different most prob. locations depen.
on voxel}
% precuneus
Two additional clusters are apparent in the ventral precuneus extending into the
retrosplenial cortex.
% LOC
Finally, two homologous clusters are located in the superior lateral occipital
cortex.

@@

% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to \citep{sengupta2016extension}, we used the same contrast of each
naturalistic stimulus and the same threshold for all subjects (Z>2.3, p<.05
cluster-corrected for the analysis in subject-space; Z>3.4, p<.05 for the
analysis in group-space).
% subject space -> NeuroVault
Results of the analyses that were performed in subject-space can be found in the
accompanying dataset.
% here report in group space
For better comparisons of subjects, we here report results from the analyses
performed in group space.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AV
and AD $t$-contrast, and the outline of overlapped, individual PPAs
\citep{sengupta2016extension}.
% MNI space
The $z$-maps and PPA outline are overlayed on the co-registered MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts [at least some] voxels of
significant clusters in almost all subjects.

@@

% Bland-Altman-Plots
To better depict the agreement and difference between the results of the visual
localizer and the primary AD contrast, we created a Bland-Altman-Plot for every
subject (see ).
% what it depicts
Each subplot of Figure \ref{fig:bland-altman} visualizes the mean value and
difference (localizer minus AD) of two spatially corresponding voxels in the
unthresholded $z$-maps.
% top KDE plot
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (see KDE plot for the x-axis).
% right KDE plot
Values above the horizontal line depict voxels that show a higher $z$-value in
the dedicated localizer, values below the horizontal line depict voxels that
show higher $z$-value in the AD stimulus.

@@

@@

% AV
In order to test the robustness of our findings, we created four additional
$t$-contrasts for the AV stimulus (see Table \ref{tab:av-contrasts}) to be
investigated on a group level.
% results: PPA; biggest overlap in posterior part of PPA group overlap  =
%temporal occipital fusiform cortex
All of the overall five AV contrasts yielded significant bilateral clusters that
overlap with the PPA group overlap (see Figure \ref{fig:stability-slices}).
% AD
For the AD stimulus, we created overall eight $t$-contrasts (see Table
\ref{tab:ao-contrasts}).
% results
All contrasts except contrast 7 (\texttt{se\_new}, \texttt{se\_old} >
non-spatial categories) and contrast 8 (\texttt{se\_new} > non-spatial
categories) yielded significant bilateral clusters in anterior regions of the
group PPA overlap (see Figure \ref{fig:stability-slices}), suggesting
a certain robustness of this result.

@@

% AD stimulus
In the analysis of the AD data, we created control contrasts based on events of
the annotated movie cuts (cf. Table \ref{tab:ao-contrasts})
% contrast 9
Contrast 9 (vse\_new > pe\_old) revealed one significant cluster in the left
inferior prefrontal cortex (pars triangularis) and right ventral
precuneus/posterior cingulate gyrus.
% contrast 12
Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
one cluster in the right posterior hippocampus.

@@

% optimal stimulus type in vision
In the visual domain, landscapes and not pictures of landmarks or buildings are
considered to be the ``optimal'' stimulus type
\citep{epstein2008parahippocampal}.
% we did not choose se\_new and se\_old
We did not include the categories that contained switches from one setting to
another (\texttt{se\_new} and \texttt{se\_old}) which one might assume to
contain the auditory equivalent to the ``optimal'' visual stimulus type in the
primary AD contrast.
% why
The reason was that the categories \texttt{se\_new} and \texttt{se\_old} were
heterogeneous: they rarely contained holistic (but also vague) descriptions of
landscapes (e.g.  ``[Forrest is running through the] jungle'') but mostly
landmarks or buildings, and also non-spatial hints (e.g. ``[Jenny as a]
teenager``).
% further studies
Given that humans can identify the gist of a rich visual scene within the
duration of a single fixation \citep{henderson2003human} further studies might
investigate if vague verbal descriptions of landscapes lead to a different
hemodynamic activity level than descriptions of more concrete parts of a scene
(e.g.``[a] beacon'', [a] ``farmhouse'').

@@

\ldots
